Minimax lower bounds for source localization

### 2017-01-22 paper.tex
Add new section on numerical bounds.

\subsection{Lower bounds using Le Cam's method}

@@

>>>>

\subsection{Lower bounds using Le Cam's method}
\label{sec:lecam-lb}

@@

\subsection{Towards a more realistic sensor model}

The bound in Theorem~\ref{thm:main-lb} indicates that the error in source
localization goes to zero, as the number of sensors goes to infinity. This
observation is distinct from the lower bound given
in~\cite{Grover2016Fundamental}, where even with an infinite number of sensors,
the lower bound is strictly greater than zero. This indicates that the bound
in section~\ref{sec:lecam-lb} is loose for large numbers of sensors.

The looseness lies in a poor sensor model: we assume that an arbitrarily large
number of sensors can be squeezed into a finite amount of space, and that these
sensors \emph{still} give us i.i.d.\ observations, with the same noise
variance. This is an impractical expectation. In reality, sensors have a
certain width, and the signal measured by them is the integral of the
continuous-space signal within that width (this is similar to a sample-and-hold
circuit, which integrates a continuous-\emph{time} signal over a short period).
If the width of a sensor is decreased, then effectively, its signal-to-noise
ratio reduces \textcolor{red}{<Need to add reference or explanation>} (this is
intuitively evident in the sample-and-hold analogy: to compute the signal
value, the integral must be divided by the time interval over which the
integration is performed; this division amplifies noise as the time interval
gets smaller).

We performed a preliminary study to understand the effect of viewing sensors
as integrators. The bounding technique used in section~\ref{sec:lecam-lb} no
longer easily admits a solution which gives a bound for all values of $m$. We
can compute the bound numerically, however, using exact expressions for error
probability in a binary hypothesis test. For gaussian distributions of equal
variance, the expression is a Q-function in the distance between their means:
\begin{equation}
	P_e = \inf_\psi \mathbb P(\psi(Y^n) \neq V) = Q\bigg(\frac{\norm{\v\mu_1 - \v\mu_2}}{2\sigma}\bigg)
\end{equation}
\textcolor{red}{Is this definitely correct? i.e.\ the best test is a linear
separator? I think this is coming from Neyman-Pearson. Should I cite?}
The minimax estimation risk is lower bounded by the risk in hypothesis testing,
so
\begin{equation}
	\mathfrak{M}_n(\mathcal{P}, \Phiorho) = \Phi(\delta) P_e = \delta^2 Q\bigg(\frac{\norm{\v x(\theta_0) - \v x(\theta_1)}}{2\sigma}\bigg).
\end{equation}
This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
separated by a distance of $2\delta$. As the $\delta$ increases, it becomes
easier to distinguish between the two hypotheses, so $P_e$ falls. When
numerically evaluating the bound, therefore, we have to \emph{manually}
trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
hypotheses to distinguish between. To make the simulation easier, we can relax
the process of finding the least discernable hypothesis pair by fixing
$\theta_0$. Then, we need only optimize over $\delta$, making the process more
tractable. This comes at the cost of loosening the lower bound.

\begin{figure}[t]
	\centering
	\includegraphics[width=3.2in]{lb-vs-numsensors-int}
	\caption{A numerically generated plot of the lower bound on minimax risk of
	source localization, against the number of uniformly distributed sensors
used to estimate the location. The different curves are for different numbers
of ``trials'' (i.i.d.\ sensor observations). The bound saturates for large $m$,
indicating that for a fixed number of trials (or equivalently, for a fixed
SNR), there is reduced benefit in increasing the number of sensors beyond a
point. However, with more trials, the bound saturates at increasingly larger
numbers of sensors. Thus, there is benefit to increasing the number of sensors,
provided SNR can be increased by leveraging larger numbers of trials.}
	\label{fig:numerical}
\end{figure}

Plotting this numerically computed bound for different numbers of trials (see
Fig.~\ref{fig:numerical}) reveals some interesting trends. First, the bound
saturates as $m$ grows large, matching the behaviour presented
in~\cite{Grover2016Fundamental}. Second, the lower bound on error is larger for
smaller numbers of sensors, as we expect. With fewer sensors, it is harder to
estimate the location of the point source. Third and most importantly, the
point at which the bound begins to saturate appears to increase when we use
more trials. Recall that the number of ``trials'' is the number of i.i.d.\
sensor observations we receive. Intuitively, estimation is eased with more
trials, as we could perform more averaging, and increase SNR. \emph{With higher
SNR, there is greater benefit in using a larger number of sensors.} This
matches the intuition given in~\cite{Grover2016Information}, where it is
propounded that using more sensors allows us to sample a greater number of
high-frequency components of the source signal, and hence get a better estimate
of its location.
